The \project{unRAVE} catalog

### 2016-08-18 article/unrave.tex
Paragraph about APOGEE giant training set

% These restrictions forced us to use a heterogeneous training set.
%

\stub{We used the APOGEE DR13 cross-over for training set stars on the giant branch with cuts XYZ}

% training set from APOGEE or K2/EPIC?!!

>>>>

These constraints forced us to construct a heterogeneous training set.  Given previous
successes in transferring high S/N ratio labels from \project{APOGEE} \citep{Ness_2015,
Ness_2016,Ho_2016,Casey_2016b}, we chose to use the 1,355 stars in the \project{APOGEE}
---\rave\ overlap sample for giant star labels in the training set.  Of these, about
900 are giants according to \project{APOGEE}.  From this sample we selected stars to
have: metallicity determinations ([Fe/H] $> -5$); high S/N ratios in both the 
\project{APOGEE} and \rave\ spectra ($>200$ in \project{APOGEE}; $>50$ in \rave); and
we further required that the \project{ASPCAP} pipeline did not report any peculiar
flags (\texttt{ASPCAPFLAG = 0}).  These restrictions left us with 357 stars along the
giant branch, with metallicities ranging from [Fe/H] $= -1.62$ to 0.32.

Assembling a training set for the main-sequence and sub-giant branch was not as
straightforward.
% training set from K2/EPIC?!!

% Identifying obviously bad stars that have been mis-classified by K2/EPIC
